\LARGE \bf Matrix Multiplication-Driven Repulsive Fields for 3D Voxel-Based Robotic Manipulator Path Planning

### 2024-03-04 Articles/IROS/root.tex
text reordering
draft primary axis weights distribution description

\subsection{CONVOLUTIONAL KERNELS}

@@

Our kernels are designed as three-dimensional matrixes with a primary kernel axis aligned along a specific Cartesian direction, corresponding to the calculated repulsive velocity. The two secondary kernel axes are orthogonal to this primary axis. The distribution of values along the primary axis is inversely symmetric, exhibiting positive values on one side and negative values on the other, with the zero valued cell in the center of the kernel, where jump between max positive and max negative magnitude is. The function of the increase in magnitude along the primary axis of the kernel defines the shape of the repulsive velocity field, determining how the repulsive velocity changes as the agent approaches an obstacle.

The length of the primary axis is critical, as it dictates the detection range for obstacles. Longer kernels can detect obstacles further away
from the robot, essentially extending the ’safety zone’ around the robot. If the primary axis is too long, it can lead to extra calculations and may cause the robot to unnecessarily avoid obstacles that aren't in its immediate path, making its movement and path planning less efficient. A kernel with a primary axis that is too short might restrict the robot's ability to maneuver, detecting obstacles potentially too late, compromising the robots capacity to avoid obstacles effectively (eq. \ref{eq: detect range}). Moreover, it is essential for the magnitudes at the kernel's periphery to be minimal, promoting a smooth increase in repulsive velocity when approaching the obstacle rather than a sudden spike.

>>>>

\comment{}{TODO: add the indexes for x,y,z directions}

\subsection{KERNELS SELECTION}

@@

Our kernels are designed as three-dimensional matrixes with a primary kernel axis aligned along a specific Cartesian direction, corresponding to the calculated repulsive velocity. The two secondary kernel axes are orthogonal to this primary axis. The distribution of values along the primary axis is inversely symmetric, exhibiting positive values on one side and negative values on the other, with the zero valued cell in the center of the kernel, where jump between max positive and max negative magnitude is. The function of the increase in magnitude along the primary axis of the kernel defines the shape of the repulsive velocity field, determining how the repulsive velocity changes as the agent approaches an obstacle. Moreover, it is essential for the magnitudes at the kernel's periphery to be minimal, promoting a smooth increase in repulsive velocity when approaching the obstacle rather than a sudden spike.

% KERNEL WEIGHTS

% PRIMARY AXIS

We propose two different primary axis weights distributions, of course there is no reason why any other distribution of weights could not be used. The choice of the weights distribution should depend on the profile of the repulsive velocities we want to archieve for the APF.

The first of the proposed functions is a mirrored normal / gaussian distribution. By changing the sigma we can control how fast or slow does the field value grow when we approach obstacles.

\begin{equation}
w_i = 
\begin{cases} 
	e^{-\frac{\Delta i^2}{2\sigma^2}} / (\sigma \sqrt{2\pi}) & \text{if } \Delta i > 0 \\
	0 & \text{if } \Delta i = 0 \\
	-e^{-\frac{\Delta i^2}{2\sigma^2}} / (\sigma \sqrt{2\pi}) & \text{if } \Delta i < 0 
\end{cases}
\end{equation}

%\begin{equation}
%w_i = 
%\begin{cases} 
%	\frac{e^{-\frac{\Delta i^2}{2\sigma^2}}}{\sigma \sqrt{2\pi}} & \text{if } \Delta i > 0 \\
%	0 & \text{if } \Delta i = 0 \\
%	-\frac{e^{-\frac{\Delta i^2}{2\sigma^2}}}{\sigma \sqrt{2\pi}} & \text{if } \Delta i < 0 
%\end{cases}
%\end{equation}

Another distribution we used is mirrored linear, where the $l=\lceil width / 2 \rceil$ is the rounded up half length of the primary axis kernel.

\begin{equation}
	w_i = 
	\begin{cases} 
	 	\frac{l - \Delta i}{l} & \text{if } \Delta i > 0 \\
		0 & \text{if } \Delta i = 0 \\
		\frac{l + \Delta i}{l}& \text{if } \Delta i < 0 
	\end{cases}
\end{equation}

% ORTHAGONAL AXIS

The length of the primary axis is critical, as it dictates the detection range for obstacles. Longer kernels can detect obstacles further away
from the robot, essentially extending the ’safety zone’ around the robot. If the primary axis is too long, it can lead to extra calculations and may cause the robot to unnecessarily avoid obstacles that aren't in its immediate path, making its movement and path planning less efficient. A kernel with a primary axis that is too short might restrict the robot's ability to maneuver, detecting obstacles potentially too late, compromising the robots capacity to avoid obstacles effectively (eq. \ref{eq: detect range}).
